---
title: "2248111_CAT2"
author: "Nishanth Girish"
date: "2023-01-24"
output: word_document
---

```{r}
#Importing necessary libraries:
library(olsrr)
library(ggplot2)
library(pROC)
library(pscl)
library(MASS)
library(car)
library(AID)
```

```{r}
#Selecting an in-built data set: surgical from the olsrr package
data1 = surgical
data1
attach(data1)    #attach to avoid using $ symbol.
```


```{r}
#1. Fitting a multiple linear regression model:
mlr = lm(y~., data = data1)
summary(mlr)
```
INTERPRETATION:

The R-squared value of the model is 0.7818 which indicates that it is a good fit. However, we observe that there are many insignificant variables such as gender, age, alc_mod. Hence, this might not be the best model that fits the data. 
Thus, we go for stepwise regression and see which variables must be selected/eliminated for our model.

```{r}
#2. Stepwise regression:

#Stepwise backward elimination:
ols_step_backward_aic(mlr,details = TRUE)

```

INTERPRETATION:

Initially, all the variables are present in the model. No variables removed.
Step 0: AIC = 736.3899 
At Step 1 : AIC = 734.4068, alc_mod variable is removed.
At Step 2 : AIC = 732.4942, gender variable is removed.
At Step 3 : AIC = 730.6204. age variable is removed.
After this no more variables are removed and the model obtained is:
 y ~ bcs + pindex + enzyme_test + liver_test + alc_heavy 

R-squared value for this model is 0.781.which indicates that it is a good fit.


```{r}
#stepwise forward selection
ols_step_forward_aic(mlr,details = TRUE)
```

INTERPRETATION:

Initially, no variables are present in the model. Only intercept term present.
Step 0: AIC = 802.606 
At Step 1 : AIC = 771.8753, liver_test variable is selected.
At Step 2 : AIC = 761.4394, alc_heavy variable is selected.
At Step 3 : AIC = 750.5089, enzyme_test variable is selected.
At Step 4 : AIC = 735.7146, pindex variable is selected.
At Step 5 : AIC = 730.6204, bcs variable is selected.

After this no more variables are selected and the model obtained is:
 y ~ bcs + pindex + enzyme_test + liver_test + alc_heavy 
R-squared value for this model is 0.781 which indicates that it is a good fit
This is the same as the model obtained after backward elimination.

We note that the R-squared value of stepwise regression model and multiple linear regression model are the same. However, in stepwise regression only the significant variables are taken into account.

```{r}
#plot:
plot(ols_step_forward_aic(mlr))

plot(ols_step_backward_aic(mlr))
```

INTERPRETATION:

The graphs show the variables selcted and eliminated respectively at each step as AIC value decrease.

```{r}
#3. Best model:

#Taking only variables selected after stepwise forward selction:
mlr_best = lm( y~ liver_test + alc_heavy + enzyme_test + pindex + bcs, data= data1) 
summary(mlr_best)
```
INTERPRETATION:

The intercept is -1178.330. The regression coefficients are 58.064,317.848, 9.748, 8.924, 59.864.
R-squared value is 0.7809 which indicates that it is a good model. Almost all the variables are statistically significant. 
This is the best linear model that can be obtained.

```{r}
#4. Logistic regression model:

#We are taking the alc_heavy as the dependent variable here as we wish to predict if a patient is a heavy drinker or not.

log_model = glm(alc_heavy ~ bcs+pindex+enzyme_test+liver_test+age+y, data= data1, family = "binomial")
log_model
```

INTERPRETATION:

The null deviance is 51.75 and residual deviance is 28.47. The AIC value is 42.47.
The difference between null deviance and residual deviance is high which means that the model is pretty good.


```{r}
#actual v/s predicted values:
prob <- predict(log_model, type = "response")
cbind(alc_heavy, round(prob,2))
```


```{r}
#confusion matrix
cutoff = ifelse(prob<0.5,"0","1")

table(alc_heavy,cutoff)
```


```{r}
#accuracy = (TP + TN )/(TP+TN+FN+FP)
accuracy = (42+5)/(42+5+5+2)
accuracy
```
INTERPRETATION:
The model is very accurate i.e it has an accuracy of 87.03%

```{r}
#pseudo R-squared value:
pR2(log_model)["McFadden"]
```
INTERPRETATION:
The model is very good since pseudo R-squared value is greater than 0.4

#4: Decisons/Suggestions:
We can use stepwise regression to determine which variables need to be selected in the model and then fit a multiple or simole linear regression model to obtain the best model.
We can use logistic rgression when there are categorical variables and we need to predict or classify.
