---
title: "2248111_Lab2"
author: "Nishanth Girish"
date: '2022-11-25'
output: word_document
---

```{r}
#Importing necessary libraries:
library(readxl)
library(GGally)
library(ggplot2)
library(psych)
```

```{r}
#Importing the data from Excel
data <- read_excel("C:/Users/nisha/Downloads/Dataset_MLR.xlsx")
head(data)           #display first few rows of the data
attach(data)         #to avoid using $ sign
```
Data Description:                                                            
The dataset shows the scores in the End Semester Examination (ESE) and the scores in two preliminary examinations CIA1 and CIA2 for 22 students in a Statistics course. It contains 4 columns: Student Reg No., ESE ,CIA1, CIA2.

```{r}
newdata= data[,c(-1,-5,-6)]  #drop the 1st,5th and 6th columns as they are                                      unnecessary.
head(newdata)
attach(newdata)
```

```{r}
#1.Matrix scatter diagram:
pairs(newdata)
ggpairs(newdata)
```
Interpretation: From the matrix scatter plot diagram, we can infer that the variables/columns are highly positively correlated to each other. 

```{r}
#Co-efficient of correlation:
cor(ESE,CIA1)      #correlation between ESE and CIA1 variables.

cor(ESE,CIA2)      #correlation between ESE and CIA2 variables.

cor(CIA1,CIA2)     #correlation between CIA1 and CIA variables.
```
Interpretation: The coefficient correlation between ESE and CIA1 variables is: 0.8956842.
The coefficient correlation between ESE and CIA2 variables is: 0.9273811.
The coefficient correlation between ESE and CIA1 variables is: 0.8841434.
We observe that the variables aare highly positively correlated.

```{r}
#2.Estimate the parameters of a multiple linear regression model and fit a regression line.

#Here, the dependent variable is the ESE column and the independent variables are 
#CIA1 and CIA2 columns. ESE is a dependent variable as the end semester marks #depends upon the internal marks obtained by a student.

model = lm(ESE ~ . ,data = newdata)   #Multiple linear regression model


summary(model) 
```
Interpretation:The regression coeeficients are 0.4883 and 0.672. The y-intercept is -14.5005  i.e it cuts or intersects the Y-axis at (-14.5005 ,0).  Hence, the regression line is given by: 
y = 0.4883*(x1)+ 0.6720*(x2) + -14.5005.
Here, y is ESE, x1 is CIA1, x2 is CIA2 respectively.
Also, R-squared value is 0.8744.

```{r}
#Residual plots:
plot(model)
```


```{r}
#3.Testing the significance of the regression coefficients
anova(model)
```
Interpretation: For CIA1 variable, p-value is 4.721e-10. Hence, we can conclude that the regression coefficient for CIA1 variable is statistically significant.
Similarly, for CIA2 variable, p-value is 0.001361. Hence, we can conclude that the regression coefficient for CIA2 variable is statistically significant.



