---
title: "Untitled"
author: "Nishanth Girish"
date: '2023-01-13'
output: word_document
---

```{r}
#Importing necessary libraries:
library(GGally)
library(ggplot2)
library(psych)
library(mctest)
library(lmtest)
library(corrplot )
library(olsrr)
```


```{r}
#Taking an inbuilt dataset from the olsrr library:
data1<- auto
attach(data1)
head(data1)
```
DATASET DESCRIPTION:
The auto dataset contains prices of automobiles along with mileage, dimensions, gears, reps/sec, turn radius and other information.
Here the price column is the dependent variable and the rest are independent variables.

```{r}
#removing column containing missing values:
data_clean <- data1[,c(-3,-11)]
```


```{r}
#Fitting a multiple linear regression model:
mlr1 = lm(price ~  . , data= data_clean)
summary(mlr1)
```



```{r}
#Fitting a stepwise forward regression value based on AIC values:
ols_step_forward_aic(mlr1, details = TRUE)
```
INTERPRETATION:
Initially at Step 0, AIC value = 1395.426. No variables selected(only intercept term taken into the model)
At Step 1, AIC = 1372.071. Weight variable selected.
At Step 2, AIC = 1364.337. Turn variable selected.
At Step3, AIC = 1363.22. Headroom variable selected.
No more variables are selected. Thus, the variables selected in forward selection are weight, turn, and headroom.
R-Squared  value of the model = 0.403


```{r}
#ols_step_backward_p(mlr1,pent=0.05, details = F)
ols_step_backward_aic(mlr1,pent=0.05,details = TRUE)
```

INTERPRETATION:
Initially at Step 0 the whole model is considered. AIC = 1363.133 
At Step 1, trunk variable is eliminated. AIC = 1362.313 
No more variables are eliminated.
R-squared value of the model is 0.471. Hence it is a better model than the stepwise forward regression model which has R-squared = 0.403

```{r}
#Plot of the stepwise forward regression model:
plot(ols_step_forward_aic(mlr1))
```

INTERPTRETATION:
From the graph we observe that the AIC values keep on decreasing as the number of steps increases and variables added at each step is shown on the graph.

```{r}
plot(ols_step_backward_aic(mlr1))
```

INTERPTRETATION:
From the graph we observe that the AIC values keep on decreasing as the number of steps increases and variables eliminated at each step is shown on the graph.

```{r}
#Fitting a linear model on the variables left in the model after  backward elimantion 
mlr1_bwd <- lm(price ~ weight + turn  + headroom + mpg +length +displacement + gear_ratio, data = data_clean)
summary(mlr1_bwd)
```
INTERPRERTATION:
The regression coeeficients are: 4.782, -314.029, -583.881, -108.609, -67.117 2284.028.The y-intercept is 11580.164.  
Also, R-squared value is  0.4709 which indicates that it is a moderate model.


```{r}
#Taking 2nd dataset:
data2<- cement
attach(data2)
data2
```

```{r}
#Fitting a multiple linear regression model:
mlr2 = lm(y ~ x1+x2+x3+x4 , data= data2)  
summary(mlr2)
```

```{r}
#Stepwise forward regression:
ols_step_forward_aic(mlr2,pent = 0.05 , details = TRUE)
```

INTERPRETATION:
Initially at Step 0, AIC value = 110.3368. No variables selected(only intercept term taken into the model)
At Step 1, AIC = AIC = 97.74404. x4 variable selected.
At Step 2, AIC = 67.63411.  x1 variable selected.
At Step3, AIC = 63.866. x2 variable selected.
No more variables are selected. Thus, the variables selected in forward selection are x4, x1, and x2.
R-Squared  value of the model = 0.982 .

```{r}
#ols_step_backward_p(mlr2, pent=0.05, details= F)
ols_step_backward_aic(mlr2,pent=0.05, details = T)
```

INTERPRETATION:
Initially at Step 0 the whole model is considered. AIC =  65.837
At Step 1, x3 variable is eliminated. AIC = 63.866 
No more variables are eliminated.
R-squared value of the model is  0.982.
```{r}
##Fitting a linear model on the variables left in the model after  backward elimantion:
mlr2_fwd = lm(y ~ x1+x2 + x4 , data= data2)
summary(mlr2_fwd)

```

INTERPRERTATION:
The regression coeeficients are: 1.4519 , 0.4161 , -0.2365.The y-intercept is 71.6483.  
Also, R-squared value is  0.9823 which indicates that it is a very good model.

```{r}
#Plot of the stepwise forward regression model:
plot(ols_step_forward_aic(mlr2))
```

INTERPTRETATION:
From the graph we observe that the AIC values keep on decreasing as the number of steps increases and variables selected at each step is shown on the graph.

```{r}
#Plot of the stepwise forward regression model:
plot(ols_step_backward_aic(mlr2))
```

INTERPTRETATION:
From the graph we observe that the AIC values keep on decreasing as the number of steps increases and variables eliminated at each step is shown on the graph.



